---
title: "datawrangling"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Wranging

I first obtained a dataset about overall ESG scores and scores of three separate dimensions (environmental, social and governance) of 1122 Chinese publicly listed firms during 2010-2020 from Bloomberg. Then, after data wranging, I obtained a tidy dataset named `ESG_bloomberg_processed`.

```{r ESG}
library(readxl)
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(agricolae) 
library(corrplot)
library(PerformanceAnalytics)
library(RColorBrewer)

ESG_bloomberg <- read_excel("./ESG.xlsx", sheet = "bloomberg")
colnames(ESG_bloomberg)

ESG_bloomberg_ESG <- ESG_bloomberg %>%
  select(stockcode, Name, ESG2020:ESG2010) %>%
  pivot_longer(ESG2020:ESG2010, names_to = "Year", values_to = "ESG_Score")
ESG_bloomberg_ESG$Year <- substring(ESG_bloomberg_ESG$Year,4,8)
ESG_bloomberg_ESG$Year <- as.numeric(ESG_bloomberg_ESG$Year)
ESG_bloomberg_ESG$Index <- "ESG"

ESG_bloomberg_E <- ESG_bloomberg %>%
  select(stockcode, Name, E2020:E2010) %>%
  pivot_longer(E2020:E2010, names_to = "Year", values_to = "ESG_Score")
ESG_bloomberg_E$Year <- substring(ESG_bloomberg_E$Year,2,6)
ESG_bloomberg_E$Year <- as.numeric(ESG_bloomberg_E$Year)
ESG_bloomberg_E$Index <- "E"
  
ESG_bloomberg_S <- ESG_bloomberg %>%
  select(stockcode, Name, S2020:S2010) %>%
  pivot_longer(S2020:S2010, names_to = "Year", values_to = "ESG_Score")
ESG_bloomberg_S$Year <- substring(ESG_bloomberg_S$Year,2,6)
ESG_bloomberg_S$Year <- as.numeric(ESG_bloomberg_S$Year)
ESG_bloomberg_S$Index <- "S"

ESG_bloomberg_G <- ESG_bloomberg %>%
  select(stockcode, Name, G2020:G2010) %>%
  pivot_longer(G2020:G2010, names_to = "Year", values_to = "ESG_Score")
ESG_bloomberg_G$Year <- substring(ESG_bloomberg_G$Year,2,6)
ESG_bloomberg_G$Year <- as.numeric(ESG_bloomberg_G$Year)
ESG_bloomberg_G$Index <- "G"

ESG_bloomberg_processed <- rbind(ESG_bloomberg_ESG, ESG_bloomberg_E, ESG_bloomberg_S, ESG_bloomberg_G)
ESG_bloomberg_processed <- pivot_wider(ESG_bloomberg_processed, names_from = Index, values_from = ESG_Score)

rm(ESG_bloomberg_ESG)
rm(ESG_bloomberg_E)
rm(ESG_bloomberg_S)
rm(ESG_bloomberg_G)


ESG_syntao <- read_excel("./ESG.xlsx", sheet = "shangdaoronglv")
```

I then obtained a dataset about basic organizational characteristics of all Chinese publicly listed firms and their financial statement information during 2010-2020 from Wind database. I obtained a tidy dataset named `Wind_processed`.

```{r Wind}

ListedFirm_Wind <- read_excel("./Firm_wind.xlsx")
#colnames(ListedFirm_Wind)

#Basic characteristics of publicly listed firms
FirmBasic <- ListedFirm_Wind %>%
  select(stockcode, Name, IPO_date, CompanyType, Province, City, IndustryName, IndustryCode)
FirmBasic$stockcode <- substring(FirmBasic$stockcode,1,6)

#Outstanding shares of Top1-Top10 shareholders/Total outstanding shares
Top1_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top1.2021:top1.2010) %>%
  pivot_longer(top1.2021:top1.2010, names_to = "Year", values_to = "Top1")
Top1_Wind$Year <- substring(Top1_Wind$Year,6,10)
Top1_Wind$Year <- as.numeric(Top1_Wind$Year)

Top2_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top2.2021:top2.2010) %>%
  pivot_longer(top2.2021:top2.2010, names_to = "Year", values_to = "Top2")
Top2_Wind$Year <- substring(Top2_Wind$Year,6,10)
Top2_Wind$Year <- as.numeric(Top2_Wind$Year)

Top3_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top3.2021:top3.2010) %>%
  pivot_longer(top3.2021:top3.2010, names_to = "Year", values_to = "Top3")
Top3_Wind$Year <- substring(Top3_Wind$Year,6,10)
Top3_Wind$Year <- as.numeric(Top3_Wind$Year)

Top4_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top4.2021:top4.2010) %>%
  pivot_longer(top4.2021:top4.2010, names_to = "Year", values_to = "Top4")
Top4_Wind$Year <- substring(Top4_Wind$Year,6,10)
Top4_Wind$Year <- as.numeric(Top4_Wind$Year)

Top5_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top5.2021:top5.2010) %>%
  pivot_longer(top5.2021:top5.2010, names_to = "Year", values_to = "Top5")
Top5_Wind$Year <- substring(Top5_Wind$Year,6,10)
Top5_Wind$Year <- as.numeric(Top5_Wind$Year)

Top6_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top6.2021:top6.2010) %>%
  pivot_longer(top6.2021:top6.2010, names_to = "Year", values_to = "Top6")
Top6_Wind$Year <- substring(Top6_Wind$Year,6,10)
Top6_Wind$Year <- as.numeric(Top6_Wind$Year)

Top7_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top7.2021:top7.2010) %>%
  pivot_longer(top7.2021:top7.2010, names_to = "Year", values_to = "Top7")
Top7_Wind$Year <- substring(Top7_Wind$Year,6,10)
Top7_Wind$Year <- as.numeric(Top7_Wind$Year)

Top8_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top8.2021:top8.2010) %>%
  pivot_longer(top8.2021:top8.2010, names_to = "Year", values_to = "Top8")
Top8_Wind$Year <- substring(Top8_Wind$Year,6,10)
Top8_Wind$Year <- as.numeric(Top8_Wind$Year)

Top9_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top9.2021:top9.2010) %>%
  pivot_longer(top9.2021:top9.2010, names_to = "Year", values_to = "Top9")
Top9_Wind$Year <- substring(Top9_Wind$Year,6,10)
Top9_Wind$Year <- as.numeric(Top9_Wind$Year)

Top10_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, top10.2021:top10.2010) %>%
  pivot_longer(top10.2021:top10.2010, names_to = "Year", values_to = "Top10")
Top10_Wind$Year <- substring(Top10_Wind$Year,7,11)
Top10_Wind$Year <- as.numeric(Top10_Wind$Year)

#Outstanding share/Total share
OutstandingShareRatio_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, OutstandingShareRatio.2021:OutstandingShareRatio.2010) %>%
  pivot_longer(OutstandingShareRatio.2021:OutstandingShareRatio.2010, names_to = "Year", values_to = "OutstandingShareRatio")
OutstandingShareRatio_Wind$Year <- substring(OutstandingShareRatio_Wind$Year,23,27)
OutstandingShareRatio_Wind$Year <- as.numeric(OutstandingShareRatio_Wind$Year)

Top10_processed <- full_join(Top1_Wind,Top2_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top3_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top4_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top5_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top6_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top7_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top8_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top9_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,Top10_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed <- full_join(Top10_processed,OutstandingShareRatio_Wind, by = c("stockcode","Name","Year"), all=T)
Top10_processed$stockcode <- substring(Top10_processed$stockcode,1,6)

rm(Top1_Wind)
rm(Top2_Wind)
rm(Top3_Wind)
rm(Top4_Wind)
rm(Top5_Wind)
rm(Top6_Wind)
rm(Top7_Wind)
rm(Top8_Wind)
rm(Top9_Wind)
rm(Top10_Wind)
rm(OutstandingShareRatio_Wind)

# chairman
Chair_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, Chairman2021:Chairman2010) %>%
  pivot_longer(Chairman2021:Chairman2010, names_to = "Year", values_to = "Chairman")
Chair_Wind$Year <- substring(Chair_Wind$Year,9,13)
Chair_Wind$Year <- as.numeric(Chair_Wind$Year)

# general manager
GM_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, GM2021:GM2010) %>%
  pivot_longer(GM2021:GM2010, names_to = "Year", values_to = "GM")
GM_Wind$Year <- substring(GM_Wind$Year,3,7)
GM_Wind$Year <- as.numeric(GM_Wind$Year)

# the number of people in the board
Board_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, Board2021:Board2010) %>%
  pivot_longer(Board2021:Board2010, names_to = "Year", values_to = "BoardNumber")
Board_Wind$Year <- substring(Board_Wind$Year,6,10)
Board_Wind$Year <- as.numeric(Board_Wind$Year)

# the number of people in the independent board
IndepBoard_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, IndepBoard2021:IndepBoard2010) %>%
  pivot_longer(IndepBoard2021:IndepBoard2010, names_to = "Year", values_to = "IndepBoardNumber")
IndepBoard_Wind$Year <- substring(IndepBoard_Wind$Year,11,15)
IndepBoard_Wind$Year <- as.numeric(IndepBoard_Wind$Year)

# the total salary of management 
ManageSalary_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ManageSalary2020:ManageSalary2010) %>%
  pivot_longer(ManageSalary2020:ManageSalary2010, names_to = "Year", values_to = "ManageSalary")
ManageSalary_Wind$Year <- substring(ManageSalary_Wind$Year,13,17)
ManageSalary_Wind$Year <- as.numeric(ManageSalary_Wind$Year)

Board_processed <- full_join(Chair_Wind,GM_Wind, by = c("stockcode","Name","Year"), all=T)
Board_processed <- full_join(Board_processed,Board_Wind, by = c("stockcode","Name","Year"), all=T)
Board_processed <- full_join(Board_processed,IndepBoard_Wind, by = c("stockcode","Name","Year"), all=T)
Board_processed <- full_join(Board_processed,ManageSalary_Wind, by = c("stockcode","Name","Year"), all=T)
Board_processed$stockcode <- substring(Board_processed$stockcode,1,6)

rm(Chair_Wind)
rm(GM_Wind)
rm(Board_Wind)
rm(IndepBoard_Wind)
rm(ManageSalary_Wind)

#Financial indices
ROA1_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ROA1.2010:ROA1.2021) %>%
  pivot_longer(ROA1.2010:ROA1.2021, names_to = "Year", values_to = "ROA1")
ROA1_Wind$Year <- substring(ROA1_Wind$Year,6,10)
ROA1_Wind$Year <- as.numeric(ROA1_Wind$Year)

ROA2_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ROA2.2010:ROA2.2021) %>%
  pivot_longer(ROA2.2010:ROA2.2021, names_to = "Year", values_to = "ROA2")
ROA2_Wind$Year <- substring(ROA2_Wind$Year,6,10)
ROA2_Wind$Year <- as.numeric(ROA2_Wind$Year)

ROE1_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ROE1.2010:ROE1.2021) %>%
  pivot_longer(ROE1.2010:ROE1.2021, names_to = "Year", values_to = "ROE1")
ROE1_Wind$Year <- substring(ROE1_Wind$Year,6,10)
ROE1_Wind$Year <- as.numeric(ROE1_Wind$Year)

ROE2_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ROE2.2010:ROE2.2021) %>%
  pivot_longer(ROE2.2010:ROE2.2021, names_to = "Year", values_to = "ROE2")
ROE2_Wind$Year <- substring(ROE2_Wind$Year,6,10)
ROE2_Wind$Year <- as.numeric(ROE2_Wind$Year)

ROIC_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ROIC2010:ROIC2021) %>%
  pivot_longer(ROIC2010:ROIC2021, names_to = "Year", values_to = "ROIC")
ROIC_Wind$Year <- substring(ROIC_Wind$Year,5,9)
ROIC_Wind$Year <- as.numeric(ROIC_Wind$Year)

ROP_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, ROP2010:ROP2021) %>%
  pivot_longer(ROP2010:ROP2021, names_to = "Year", values_to = "ROP")
ROP_Wind$Year <- substring(ROP_Wind$Year,4,8)
ROP_Wind$Year <- as.numeric(ROP_Wind$Year)

FinancialPerf_processed <- full_join(ROA1_Wind,ROA2_Wind, by = c("stockcode","Name","Year"), all=T)
FinancialPerf_processed <- full_join(FinancialPerf_processed,ROE1_Wind, by = c("stockcode","Name","Year"), all=T)
FinancialPerf_processed <- full_join(FinancialPerf_processed,ROE2_Wind, by = c("stockcode","Name","Year"), all=T)
FinancialPerf_processed <- full_join(FinancialPerf_processed,ROIC_Wind, by = c("stockcode","Name","Year"), all=T)
FinancialPerf_processed <- full_join(FinancialPerf_processed,ROP_Wind, by = c("stockcode","Name","Year"), all=T)
FinancialPerf_processed$stockcode <- substring(FinancialPerf_processed$stockcode,1,6)

rm(ROA1_Wind)
rm(ROA2_Wind)
rm(ROE1_Wind)
rm(ROE2_Wind)
rm(ROIC_Wind)
rm(ROP_Wind)

#structure characteristics
LEV_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, LEV2010:LEV2021) %>%
  pivot_longer(LEV2010:LEV2021, names_to = "Year", values_to = "LEV")
LEV_Wind$Year <- substring(LEV_Wind$Year,4,8)
LEV_Wind$Year <- as.numeric(LEV_Wind$Year)

CurrentAssetsRatio_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, CurrentAssetsRatio2010:CurrentAssetsRatio2021) %>%
  pivot_longer(CurrentAssetsRatio2010:CurrentAssetsRatio2021, names_to = "Year", values_to = "CurrentAssetsRatio")
CurrentAssetsRatio_Wind$Year <- substring(CurrentAssetsRatio_Wind$Year,19,23)
CurrentAssetsRatio_Wind$Year <- as.numeric(CurrentAssetsRatio_Wind$Year)

CurrentLiabilityRatio_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, CurrentLiabilityRatio2010:CurrentLiabilityRatio2021) %>%
  pivot_longer(CurrentLiabilityRatio2010:CurrentLiabilityRatio2021, names_to = "Year", values_to = "CurrentLiabilityRatio")
CurrentLiabilityRatio_Wind$Year <- substring(CurrentLiabilityRatio_Wind$Year,22,26)
CurrentLiabilityRatio_Wind$Year <- as.numeric(CurrentLiabilityRatio_Wind$Year)

CurrentRatio_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, CurrentRatio2010:CurrentRatio2021) %>%
  pivot_longer(CurrentRatio2010:CurrentRatio2021, names_to = "Year", values_to = "CurrentRatio")
CurrentRatio_Wind$Year <- substring(CurrentRatio_Wind$Year,13,17)
CurrentRatio_Wind$Year <- as.numeric(CurrentRatio_Wind$Year)

Assets_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, Assets2010:Assets2021) %>%
  pivot_longer(Assets2010:Assets2021, names_to = "Year", values_to = "TotalAssets")
Assets_Wind$Year <- substring(Assets_Wind$Year,7,11)
Assets_Wind$Year <- as.numeric(Assets_Wind$Year)

Liability_Wind <- ListedFirm_Wind %>%
  select(stockcode, Name, Liability2010:Liability2021) %>%
  pivot_longer(Liability2010:Liability2021, names_to = "Year", values_to = "TotalLiabilities")
Liability_Wind$Year <- substring(Liability_Wind$Year,10,14)
Liability_Wind$Year <- as.numeric(Liability_Wind$Year)

Structure_processed <- full_join(LEV_Wind,CurrentAssetsRatio_Wind, by = c("stockcode","Name","Year"), all=T)
Structure_processed <- full_join(Structure_processed,CurrentLiabilityRatio_Wind, by = c("stockcode","Name","Year"), all=T)
Structure_processed <- full_join(Structure_processed,CurrentRatio_Wind, by = c("stockcode","Name","Year"), all=T)
Structure_processed <- full_join(Structure_processed,Assets_Wind, by = c("stockcode","Name","Year"), all=T)
Structure_processed <- full_join(Structure_processed,Liability_Wind, by = c("stockcode","Name","Year"), all=T)
Structure_processed$stockcode <- substring(Structure_processed$stockcode,1,6)

rm(LEV_Wind)
rm(CurrentAssetsRatio_Wind)
rm(CurrentLiabilityRatio_Wind)
rm(CurrentRatio_Wind)
rm(Assets_Wind)
rm(Liability_Wind)

#Combine all datasets
Wind_processed <- left_join(ESG_bloomberg_processed,FinancialPerf_processed, by = c("stockcode","Year"), all=T)
Wind_processed = Wind_processed[,-2] 
Wind_processed$Name <- Wind_processed$Name.y
Wind_processed = Wind_processed[,-7] 
Wind_processed <- left_join(Wind_processed,Top10_processed, by = c("stockcode","Name", "Year"), all=T)
Wind_processed <- left_join(Wind_processed,Board_processed, by = c("stockcode","Name", "Year"), all=T)
Wind_processed <- left_join(Wind_processed,Structure_processed, by = c("stockcode","Name","Year"), all=T)
Wind <- right_join(FirmBasic,Wind_processed, by = c("stockcode","Name"), all=T)
```

I use the dataset named `Wind_processed` and create new variables to measure ownership concentration and firm structure, finally obtaining the dataset named `Wind`.

```{r Dataset}

library("dummies")
Wind$ChairisGM <- as.numeric(Wind$Chairman == Wind$GM)
Wind$Top1sq <- (Wind$Top1)^2
Wind$Top123 <- Wind$Top1 + Wind$Top2 + Wind$Top3
Wind$Top123sq <- (Wind$Top123)^2
Wind$Top12345 <- Wind$Top123 + Wind$Top4 + Wind$Top5
Wind$Top12345sq <- (Wind$Top12345)^2
Wind$Top1.10 <- Wind$Top12345 + Wind$Top6 + Wind$Top7 + Wind$Top8 + Wind$Top9 + Wind$Top10
Wind$Top25.Top1 <- (Wind$Top12345-Wind$Top1)/Wind$Top1
Wind$Top25.Top1sq <- (Wind$Top25.Top1)^2
Wind$Top210.Top1 <- (Wind$Top1.10-Wind$Top1)/Wind$Top1
Wind$Top210.Top1sq <- (Wind$Top210.Top1)^2
Wind$Size <- log(Wind$TotalAssets)
Wind$IndepBoardRatio <- Wind$IndepBoardNumber/Wind$BoardNumber

Wind.Stateowned <- Wind %>%
  filter(CompanyType == "中央国有企业" | CompanyType == "地方国有企业") %>%
  mutate(StateOwned = 1)
Wind.NotStateowned <- Wind %>%
  filter(CompanyType != "中央国有企业" | CompanyType != "地方国有企业") %>%
  mutate(StateOwned = 0)
Wind <- rbind(Wind.Stateowned, Wind.NotStateowned)

rm(Wind.Stateowned)
rm(Wind.NotStateowned)

Wind$Industry1st <- substring(Wind$IndustryCode,1,1)
Wind20152020 <- Wind %>%
  filter(Year %in% c(2015:2020))

lm1 <- lm(ESG ~ Top1 + Top1sq + Top25.Top1 + Size + LEV + CurrentRatio + IndepBoardRatio + ChairisGM + factor(Year) + factor(IndustryCode) + factor(StateOwned), data=Wind)
summary(lm1)

lm2 <- lm(ESG ~ Top1 + Top1sq + Top25.Top1 + Size + LEV + CurrentRatio + IndepBoardRatio + ChairisGM + ROA2 + factor(Year) + factor(IndustryCode) + factor(StateOwned), data=Wind20152020)
summary(lm2)

lm3 <- lm(ESG_bloomberg_processed$ESG ~ ESG_bloomberg_processed$E + ESG_bloomberg_processed$S + ESG_bloomberg_processed$G)
summary(lm3)

#library(plm)
#lm2 <- plm(ESG ~ Top1 + Top123 + Top12345 + Top24.Top1 + Top210.Top1 + Size + IndepBoardRatio + ChairisGM, data = ESG.Str.Fin, index = c("CompanyType", "Year", "IndustryCode"), model = "within")
```

## Including Plots

I can also embed plots, for example:

```{r plots, echo=FALSE}

#Wind_trend <- Wind %>%
#  group_by(CompanyType, Year) %>%
#  filter(!is.na(ESG) & !is.na(CompanyType)) %>%
#  summarise(meanESG = mean(ESG))

summary(Wind$ESG)

library(showtext)
font_files()
showtext_auto(enable = TRUE)
font_add('Songti', 'Songti.ttc')
quartz(family='Songti')

plot1 <- ggplot(ESG_trend) +
  geom_point(aes(x = as.factor(Year), y = meanESG, color=CompanyType)) +
  xlab("Year")
print(plot1)

plot1.1 <- ggplot(ESG_trend) +
  geom_boxplot(aes(x = as.factor(Year), y = meanESG)) +
  xlab("Year") +
  facet_wrap(vars(CompanyType), ncol = 4) 
print(plot1.1)

plot2 <- ggplot(Wind) +
  geom_point(aes(x = Top1, y = ESG), alpha=0.5, size =0.5) +
  facet_wrap(vars(StateOwned)) 
print(plot2)

plot2.1 <- ggplot(Wind) +
  geom_point(aes(x = Top1, y = ESG), alpha=0.5, size =0.5) +
  facet_wrap(vars(CompanyType)) 
print(plot2.1)

plot3 <- ggplot(Wind) +
  geom_point(aes(x = Top123, y = ESG), alpha=0.5, size =0.5) +
  facet_wrap(vars(CompanyType)) 
print(plot3)

plot3.1 <- ggplot(Wind) +
  geom_point(aes(x = Top12345, y = ESG, color=CompanyType), alpha=0.7, size =0.5) 
print(plot3.1)

plot3.2 <- ggplot(Wind) +
  geom_point(aes(x = Top1, y = ESG), alpha=0.7, size =0.7) +
  ylim(0,50)
print(plot3.2)

ggplot(Wind) +
  geom_point(aes(x = LEV, y = ESG), alpha=0.7, size =0.7) +
  ylim(5,60) +xlim(0,100)

ggplot(Wind) +
  geom_point(aes(x = Top25.Top1, y = ESG), alpha=0.7, size =0.7) +
  ylim(5,60) +xlim(0,4)

ggplot(Wind) +
  geom_point(aes(x = Top210.Top1, y = ESG), alpha=0.7, size =0.7) +
  ylim(5,60) +xlim(0,5)

ggplot(Wind) +
  geom_point(aes(x = ROA2, y = ESG), alpha=0.7, size=0.5) +
  ylim(10,60) + xlim(-50,50) + facet_wrap(vars(Industry1st), ncol=6) 

ggplot(subset(Wind, Industry1st == "C"), aes(x = ROA2, y = ESG)) +
  geom_point(alpha=0.7, size=0.5) +
  ylim(10,60) + xlim(-50,50)

ggplot(subset(Wind, Industry1st == "C"),aes(x = Top1, y = ESG)) +
  geom_point(alpha=0.7, size=0.5) +
  geom_smooth(method = lm) +
  ylim(10,50) + xlim(0,100)

plot3.3 <- ggplot(Wind20152020) +
  geom_point(aes(x = Top12345, y = ESG), alpha=0.7, size =0.5) 
print(plot3.3)

plot3.4 <- ggplot(Wind20152020) +
  geom_point(aes(x = Top25.Top1, y = ESG), alpha=0.7, size =0.7) 
print(plot3.4)

plot4 <- ggplot(Wind20152020) +
  geom_boxplot(aes(x = as.factor(ChairisGM), y = ESG)) 
print(plot4)

plot4.1 <- ggplot(Wind20152020) +
  geom_boxplot(aes(x = as.factor(ChairisGM), y = ESG, color=as.factor(StateOwned)))
print(plot4.1)

plot5 <- ggplot(Wind) +
  geom_point(aes(x = IndepBoardRatio, y = ESG), alpha=0.7, size =0.5) 
print(plot5)

plot6 <- ggplot(Wind20152020) +
  geom_point(aes(x = Top1.10, y = ROA2), alpha=0.7, size =0.7) +
  ylim(-25,25)
print(plot6)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
